Data preparation for team category analysis

### 2023-05-17 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Added modal size of team, proportion of team exiting, proportion of observation window the team existed, and proportion of working days at least two team members were co-located

@@

<!-- -   Modal size of team over observation window -->

<!-- -   Proportion of team members working days remote by the day of the -->
<!--     week -->

<!-- -   Proportion of team members exiting team -->

<!-- -   Proportion of working days at least two team member co-located -->

@@

<!-- -   Proportion of observation window the team existed. -->

>>>>

### Modal size of team over observation window

Calculate the mode team size for each `supervisor_e_mail_address`.

```{r}
prep_xx <- 
  prep_a %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(team_size_mode = getmode(team_size)) %>% 
  ungroup()
```

### Proportion of team members exiting team

Calculate the number of days and last day of team members by `supervisor_e_mail_address`, and `person_id`.

```{r}
prep_a <- 
  cohort_panel %>% 
  group_by(supervisor_e_mail_address,person_id) %>% 
  summarise(days = n_distinct(date),
            last_day = max(date)) %>% 
  ungroup()
```

Identify team members that exit by limiting the list above to those who had few than the maximum number of days and whose last day was before the maxium day in the dataframe, then count the number per `supervisor_e_mail_address`.

```{r}
prep_b <- 
  prep_a %>% 
  filter(days < max(days)) %>% 
  filter(last_day < max(last_day)) %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(employee_exits = n_distinct(person_id)) %>% 
  ungroup()
```

Attach to `prep_building` selecting `supervisor_e_mail_address` and `team_members` from that dataframe to calucalate the proportio of the team exiting.

```{r}
prep_c <- 
  prep_building %>% 
  select(supervisor_e_mail_address, team_members) %>% 
  distinct() %>% 
  left_join(prep_b) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  mutate(
    employee_exits_prop = employee_exits/team_members
  )
```

Remove `team_members`.

```{r}
prep_xx <- 
  prep_c %>% 
  select(-team_members)
```

### Proportion of observation window the team existed

Calculate the number of days and last day of team members by `supervisor_e_mail_address`.

```{r}
prep_a <- 
  cohort_panel %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(team_days = n_distinct(date)) %>% 
  ungroup()
```

Calculate the number of days and last day of team members by `supervisor_e_mail_address`.

```{r}
prep_xx <- 
  prep_a %>% 
  mutate(
    team_days_prop = team_days/observation_window_days
  )
```

### Proportion of working days at least two team members co-located

Count dates where co-location occurs by `supervisor_e_mail_address`.

```{r}
prep_c <- 
  prep_b %>% 
  group_by(supervisor_e_mail_address) %>% 
  summarise(days_colocated_1 = n_distinct(date)) %>% 
  ungroup()
```

```{r}
prep_xx <- 
  prep_c %>% 
  full_join(prep_building %>% 
              select(supervisor_e_mail_address,working_days)) %>% 
  mutate(days_colocated_1_working_prop = days_colocated_1/working_days,
         days_colocated_1_observation_prop = days_colocated_1/observation_window_days) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  select(-working_days)
```

@@

@@
